---
title: "EDH descriptive stats"
author: "Petra Hermankova"
date: "06/08/2020"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
---

```{r setup, echo=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE)
devtools::install_github("mplex/cedhar", subdir="pkg/sdam")
#install.packages("tidyverse")
#install.packages("getPass")
#install.packages("formatR")
#install.packages("Hmisc")

library(tidyverse)
library(tidytext)
library(sdam)
library(jsonlite)
library(getPass)
library(formatR)
library(Hmisc)
library(purrr)
```

# Loading data

1. Input your sciencedata.dk username - type directly into the RStudio console
```{r, echo = FALSE }
user <- readline("your sciencedata username: ")
```

2. Make the request (you will be asked for password in a new pop-up window)

```{r, echo = FALSE }
resp = request("EDH_cleaned_2020-06-26.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/EDH/", method="GET", cred=c(user, getPass("your sciencedata password: ")))
```


3. Make a list from the request and display the first six records (head)
```{r}
  list_json <- jsonlite::fromJSON(resp)
  EDH_tibble = as_tibble(list_json)
```

# What is in the dataset? Descriptive stats

## Total number of inscriptions
```{r}
describe(unlist(EDH_tibble$id))
```

```{r}
total<- nrow(EDH_tibble)
total
```

## Total number of inscriptions by language
```{r}
language<- as.data.frame(table(unlist(EDH_tibble$language)))
language<- language %>% 
  mutate(Percentage = Freq/(total/100))
language$Percent_round<- round(language$Percentage, digits = 2)
```

## Date

### How many % inscription has a start date
```{r}
not_before<- as.data.frame(unlist(EDH_tibble$not_before))
nrow(not_before)
nrow(not_before)/(total/100) 
```

### How many % inscription has an end date
```{r}
not_after<- as.data.frame(unlist(EDH_tibble$not_after))
nrow(not_after)
nrow(not_after)/(total/100)
```

### Earliest date
```{r}
describe(as.numeric(not_before$`unlist(EDH_tibble$not_before)`))
```

### Latest date
```{r}
describe(as.numeric(not_after$`unlist(EDH_tibble$not_after)`))
```

### Additional dating information available through the 'commentary'
```{r}
date_info <- EDH_tibble %>% 
  select(id, not_before, not_after, commentary, origdate_text, year_of_find) 

date_commentary <- date_info %>% 
  filter(commentary != "list()" )
date_commentary

nrow(date_commentary)
nrow(date_commentary)/(total/100)

str_subset(date_commentary$commentary, "Datierung")
```


### Number of inscriptions having both not_before and not_after date
```{r}
date_info_complete <- date_info %>% 
  filter(not_before !="list()") %>% 
  filter(not_after !="list()") 
nrow(date_info_complete)
```




## Location

```{r}
location<- EDH_tibble %>% 
  select(id, coordinates, findspot_ancient, province_label, province_label_clean, province_label_certainty, country, modern_region, findspot_modern, findspot, present_location, edh_geography_uri, commentary)
```

### How many inscriptions have spatial coordinates
```{r}
coordinates <-as.data.frame(unlist(location$coordinates))
nrow(coordinates)/(total/100)
```
### Known ancient findspot
```{r}
describe(unlist(location$findspot_ancient))
```
```{r}
ancient_findspot <- as.data.frame(unlist(location$findspot_ancient))
nrow(ancient_findspot)/(total/100)
```

#### Uncertain ancient findspot (?)
```{r}
ancient_findspot_uncert <- as.data.frame(str_subset(ancient_findspot$`unlist(location$findspot_ancient)`, "\\?"))
nrow(ancient_findspot_uncert)/(total/100)
```

### Information about province
```{r}
nrow(dplyr::filter(location, location$province_label_clean != "unknown"))/(total/100)
```

#### Uncertain Roman province
```{r}
nrow(dplyr::filter(location, location$province_label_certainty == "Uncertain"))/(total/100)
province_uncert<- dplyr::filter(location, location$province_label_certainty == "Uncertain")

# what is the present day location of inscriptions with an uncertain province
table(unlist(province_uncert$present_location))

# how many of them are from Rome
str_subset(province_uncert$present_location, "Roma") 
```

#### Unknown province
```{r}
nrow(dplyr::filter(location, location$province_label_clean == "unknown"))/(total/100)
```

### Inscriptions with no coordinates available
```{r}
no_coords <- location %>% 
  filter(coordinates == "list()")
```

#### number of inscriptions with no coordinates but with ancient findspot known
```{r}
no_coords_findspot_anc <- no_coords %>% 
  filter(findspot_ancient != "list()")

nrow(no_coords_findspot_anc)
nrow(no_coords_findspot_anc)/(total/100)
```

#### number of inscriptions with no coordinates and ancient findspot unknown
```{r}
no_coords_no_findspot_anc <- no_coords %>% 
  filter(findspot_ancient == "list()")
nrow(no_coords_no_findspot_anc)
nrow(no_coords_no_findspot_anc)/(total/100)
```

#### number of inscriptions with no coordinates, unknwon ancient findspot but know modern findspot
```{r}
no_coords_findspot_mod <- no_coords_no_findspot_anc %>% 
  filter(findspot_modern != "list()")
nrow(no_coords_findspot_mod)
nrow(no_coords_findspot_mod)/(total/100)
```

#### number of inscriptions with no coordinates, no ancient nor modern findspot known
```{r}
no_coords_no_findspot_a_m <- no_coords_no_findspot_anc %>% 
  filter(findspot_modern == "list()")
nrow(no_coords_no_findspot_a_m)
nrow(no_coords_no_findspot_a_m)/(total/100)
```

#### inscriptions with no coordinates, no ancient nor modern findspot, but with known present location
```{r}
no_coords_present_location <- no_coords_no_findspot_a_m %>% 
  filter(present_location != "list()" & present_location != "lost")
nrow(no_coords_present_location)
nrow(no_coords_present_location)/(total/100)
```

##### How many inscriptions with only present day location are from museums or private collections in total numbers and percentages
```{r}
nrow(as.data.frame(str_subset(no_coords_present_location$present_location, "Mus|Muz")))
nrow(as.data.frame(str_subset(no_coords_present_location$present_location, "Mus|Muz")))/(nrow(no_coords_present_location)/100)
nrow(as.data.frame(str_subset(no_coords_present_location$present_location, "Mus|Muz")))/(total/100)


nrow(as.data.frame(str_subset(no_coords_present_location$present_location, "Priv")))
nrow(as.data.frame(str_subset(no_coords_present_location$present_location, "Priv")))/(nrow(no_coords_present_location)/100)
nrow(as.data.frame(str_subset(no_coords_present_location$present_location, "Priv")))/(total/100)
```


#### number of inscriptions with no coordinates, no ancient nor modern findpot known, nor their present location
```{r}
no_coords_no_findspot_a_m_no_present <- no_coords_no_findspot_a_m %>% 
  filter(present_location == "list()" | present_location == "lost")
nrow(no_coords_no_findspot_a_m_no_present)
nrow(no_coords_no_findspot_a_m_no_present)/(total/100)
```

#### inscriptions with no coordinates, no ancient or modern findspot or present location, only with province information
```{r}
no_coords_province<- no_coords_no_findspot_a_m_no_present %>% 
  filter(province_label_clean != "list()" & province_label_clean != "unknown")
nrow(no_coords_province)
nrow(no_coords_province)/(total/100)


no_coords_province_unknown <- no_coords_no_findspot_a_m_no_present %>% 
  filter(province_label_clean == "unknown")
nrow(no_coords_province_unknown)
```
#### inscriptions with no coordinates, no ancient or modern findspot or present location, only with modern country information
```{r}
no_coords_country<- no_coords_no_findspot_a_m_no_present %>% 
  filter(country != "list()" & country != "unknown")
nrow(no_coords_country)
nrow(no_coords_country)/(total/100)
```


#### inscriptions with no spatial information, not even province or modern country
```{r}
no_spatial_info<- no_coords_no_findspot_a_m_no_present %>% 
  filter(province_label_clean == "unknown" & country == "unknown")
nrow(no_spatial_info)
nrow(no_spatial_info)/(total/100)
```
##### inscriptions with no spatial info but with commentary addressing their origin

```{r}
unique(no_spatial_info$commentary)
```

### Checking the precision of spatial coordinates with individual spatial info (ancient findspot, modern findspot, present location etc) 
```{r}
# ancient findspot
coords_anc_findspot<- as.data.frame(cbind(id = location$id, coordinates = location$coordinates,findspot_ancient = location$findspot_ancient))

coords_anc_findspot<- coords_anc_findspot %>% 
  dplyr::filter(coordinates != "list()" & findspot_ancient != "list()")

lat_long_anc_findspot<- coords_anc_findspot %>% 
  separate(col = coordinates, into = c("latitude", "longitude"), sep = ",")

lat_long_anc_findspot$latitude <- as.numeric(lat_long_anc_findspot$latitude)
lat_long_anc_findspot$longitude <- as.numeric(lat_long_anc_findspot$longitude)
```

### Creating a map with ancient findspots to check the precision of coordinates
```{r}
library(leaflet)
```

```{r}
map_ancient_findspot <-leaflet() %>%
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  #addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>%
  addMarkers(lng = lat_long_anc_findspot$longitude, 
             lat = lat_long_anc_findspot$latitude,
             popup = paste0("<b> InscriptionID: </b>", lat_long_anc_findspot$id, 
                            "<br><b> Ancient Findspot: </b>", lat_long_anc_findspot$findspot_ancient),
    clusterOptions = markerClusterOptions()
  )
map_ancient_findspot
```






