---
title: "Working with EDH data"
subtitle: "Minimal Example: how to load the dataset"
author: "Petra Hermankova"
date: "22/09/2020"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_depth: 3
---

```{r setup, echo=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE)
devtools::install_github("sdam-au/sdam")

library(tidyverse)
library(sdam)
library(jsonlite)
library(getPass)
```

# Loading data as anonymous use (no credentials needed)

Please ignore and close the pop-up window asking for username and login. The data will then download itself without login credentials.
```{r}
resp = request("EDH_attrs_cleaned_2020-09-22.json", path="/public/b6b6afdb969d378b70929e86e58ad975", method="GET")
```

# ALTERNATIVE: Loading data with Sciencedata.dk login credentials

1. Input your sciencedata.dk username - type directly into the RStudio console

```{r, echo = FALSE }
user <- readline("your sciencedata username: ")
```

2. Make the request (you will be asked for password in a new pop-up window)

```{r, echo = FALSE }
resp = request("EDH_attrs_cleaned_2020-09-22.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/EDH/public", method="GET", cred=c(user, getPass("your sciencedata password: ")))
```


# Make a tibble from the request and display the first six records (head)

```{r}
list_json <- jsonlite::fromJSON(resp)
EDH_tibble = as_tibble(list_json)
head(EDH_tibble)
```

# Work with the data

For examples of how to work with the dataset in R, see e.g. other EDH_ETL R scripts(https://github.com/sdam-au/EDH_ETL/tree/master/scripts) or EDH_exploration R scripts(https://github.com/sdam-au/EDH_exploration).
